Very simplified likelihood

### 2024-02-21 inst/very_simplified_likelihood.Rmd
use hyper3()

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("hyper2")
library("pracma")
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("hyper2")
library("pracma")
library("magrittr")
```

@@

```{r usehyper3}
a <- seq(from=0,to=1,by=0.01)
fhyper3 <- function(r,n){
  out <- hyper3()
  out['a'] <- 1
  out['b'] <- r
  for(i in (n-r):n){
    out[c(a=1,b=i)] %<>% dec
  }
  return(out)
}

plot(NA,xlim=c(0,1),ylim=c(0,1),type='n')
M <- cbind(a=a,b=1-a)
for(r in 0:7){
  y <- loglik(M,fhyper3(r,n),log=FALSE)
  y <- y/max(y, na.rm=TRUE)
points(M[,2],y,type="l",lwd=8)
}
```
